---
title: "Assignment 3: Promotions Management"
author: "Group 11: Christina Wang, Kailin Fu, Shun Guan, Sylvia Lu, Yiran Huang"
date: "April 20, 2020"
output:
  pdf_document:
    number_sections: yes
    toc: yes
urlcolor: blue
graphics: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, message = FALSE, eval = TRUE,
                      fig.width = 4.5, fig.height = 3, fig.align = "right")
```

\setlength{\parskip}{6pt}
\newpage

# Promotional event planning
1. Evidence for strong seasonal demand
There is a strong seasonal demand for this product. Per event summary, the product has a much higher demand around the time of event 2. The base case for event 2 is 1,360, a 87% increase from event 1, a 469% increase from event 3, a 203% increase from event 4, and a 308% increase from event 5. Similarly, the base demand around event 1 is also higher than other events except event 2. The higher base demands around the time of event 2 and event 1 show a strong seasonal demand.

2. Incremental sales response
```{r}
eventsummary = data.frame(baseQ = c(728, 1360), baseP = c(2.31, 2.31), promoQ = c(1129, 2303), promoP = c(1.99, 2.31))
eventsummary$baseRev = eventsummary$baseQ*eventsummary$baseP
eventsummary$promoRev = eventsummary$promoQ*eventsummary$promoP
eventsummary$incrRevFrac = (eventsummary$promoRev - eventsummary$baseRev)/eventsummary$baseRev
print(eventsummary)
```
Per summary Table, the incremental sales response for event 1 is 33.60% and for event 2 is 69.33%.

3. Profitability results
From ROI per event summary, event 5 is the most profitable with a ROI of 53%. Event 2 is the second, with a ROI of 44%. Event 1 does not have a profitable result with the promotion, with a negative ROI of -2%. Event 3, and 4 are even worse with much more negative ROIs of -22% and -79%.

4. The profitability with forward buying
```{r}
eventsummary2 = data.frame(incrContr = c(8019, 18874), VC = c(4740, 9674), FC = c(2500, 2500))
eventsummary2$ForwardBuyCost = c(962*2, 962*2)
eventsummary2$eventCost = eventsummary2$VC + eventsummary2$FC + eventsummary2$ForwardBuyCost
eventsummary2$grossContr = eventsummary2$incrContr - eventsummary2$eventCost
eventsummary2$ROI = eventsummary2$grossContr/eventsummary2$incrContr
print(eventsummary2)
```
The profit for event 1 will be -1145 with a ROI of -14.28% and for event 2 will be 4776 with a ROI of 25.30%.

5. The approaches to calculate ROIs
The Booz Allen Hamilton (BAH) approach and the one took in class are equally good. The BAH method is more applicable when considering each unit sale, while the one took in class is more generally applicable.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

\newpage


# Estimating lift factors and promotion ROI analysis

In this part of the assignment, we analyze the effectiveness and ROI of different promotions for Hellman’s 32 oz Mayonnaise. The analysis is based on account level data at Jewel-Osco and Dominick’s Finer Foods in Chicago.
Use the table (data frame) hellmans_df in the file Hellmans.RData. hellmans_DF contains the following variables: \newline
• account \newline
• product \newline
• week \newline
• units \newline
• dollars \newline
• feature_pctacv \newline
• display_pctacv \newline

\medskip


## Question 1
Create a price variable for Hellman’s 32oz mayo. Then, although not strictly necessary (because the estimated coefficients will scale in a linear regression), you should divide the feature and display columns (variables) by 100.
Examine the feature and display variables. Provide summary statistics (number of observations, mean, standard deviation) and histograms of these variables, separately for both accounts. To what extent do these two promotional instruments differ?
Calculate the correlations between feature_pctacv, display_pctacv, and price (use the cor function in R). Comment on your findings. Do the correlations indicate a potential problem for your regression analysis to be performed below?


```{r, include = FALSE}
    library(ggplot2)
    library(tidyverse)
    library(dplyr)
    library(tidyr)
    library(lfe)
    load("Hellmans.RData")
```

```{r, fig.width = 6, fig.height = 3, fig.align = "center"}

hellmans_df$price = hellmans_df$dollars / hellmans_df$units
hellmans_df$feature = hellmans_df$feature_pctacv / 100
hellmans_df$display = hellmans_df$display_pctacv / 100

my_summary <- function(df, account) {
  df_local = df[df$account == account,]
    list("Feature Summary" = 
       list("count" = length(df_local$feature),
            "mean" = mean(df_local$feature),
            "sd" = sd(df_local$feature)),
       "Display Summary" = 
       list("count" = length(df_local$display),
            "mean" = mean(df_local$display),
            "sd" = sd(df_local$display)))
}

D_summary = my_summary(hellmans_df, "Dominicks")
J_summary = my_summary(hellmans_df, "Jewel")
print(D_summary)
print(J_summary)

hellmans_df %>% 
ggplot(data = ., aes(x=feature, color=account)) + geom_histogram(fill="white") + facet_grid(cols = vars(account))

hellmans_df %>% 
ggplot(data = ., aes(x=display, color=account)) + geom_histogram(fill="white") + facet_grid(cols = vars(account))


#Correlations
cor(hellmans_df$feature_pctacv, hellmans_df$display_pctacv)

cor(hellmans_df$feature_pctacv, hellmans_df$price)

cor(hellmans_df$display_pctacv, hellmans_df$price)
```



\newpage

## Question 2
Estimate the log-linear demand model separately for each account, using price as the only explanatory variable. Then add the feature and display variables.
Comment on the difference between the two regressions in terms of goodness of fit, and the price elasticity estimates. Is the change in price elasticity estimates as expected? What is the reason for this change? Are the coefficient estimates similar for both accounts?


```{r, fig.width = 6, fig.height = 3, fig.align = "center"}

D_lm = 
hellmans_df %>% 
filter(account == "Dominicks") %>% 
glm(log(units) ~ log(price), data = .)

summary(D_lm)

J_lm = 
hellmans_df %>% 
filter(account == "Jewel") %>% 
glm(log(units) ~ log(price), data = .)

summary(J_lm)

#Two linear model demand-price graph
hellmans_df %>% 
ggplot(data = ., aes(x= log(units), y = log(price), color=account)) + geom_point(size = 1, alpha = 1) +
  facet_grid(cols = vars(account)) + geom_smooth(method = "lm", se = FALSE)

#Compare with the feature add model

D_d_lm = 
hellmans_df %>% 
filter(account == "Dominicks") %>% 
glm(log(units) ~ log(price) + display, data = .)
summary(D_d_lm)

J_d_lm = 
hellmans_df %>% 
filter(account == "Jewel") %>% 
glm(log(units) ~ log(price) + display, data = .)
summary(J_d_lm)

D_d_f_lm = 
hellmans_df %>% 
filter(account == "Dominicks") %>% 
glm(log(units) ~ log(price) + display + feature, data = .)
summary(D_d_f_lm)

J_d_f_lm = 
hellmans_df %>% 
filter(account == "Jewel") %>% 
glm(log(units) ~ log(price) + display + feature, data = .)
summary(J_d_f_lm)

# add display improve the model, reduce deviance. However, add feature just improve it a little bit, since feature and display has high correlation. The elastict drop from 4.5 to 1.8 to 1.1 around for both account. We can consider display and feature are ommited variables for the first model.
```

\newpage

## Question 3
Consider the following three promotions: \newline
(a) 15% TPR \newline
(b) 15% TPR, 70% display \newline
(c) 15% TPR, 70% display, 100% feature \newline
Calculate the lift factors for each promotion for both accounts, based on the regression estimates in 2. Set estimates that are not statistically significant = 0.

```{r, fig.width = 6, fig.height = 3, fig.align = "center"}
lift_factor <- function(model, TPR = 0, DIS = 0, FEA = 0) {
  alpha  = if(summary(model)$coef[1,4] < 0.1) {summary(model)$coef[1,1]} else {0}
  
  beta_lp  = if(summary(model)$coef[2,4] < 0.1) {summary(model)$coef[2,1]} else {0}
#  print(beta_lp)
  
  beta_d  = 
if(length(summary(model)$coef[,1]) >= 3 ){
  if(summary(model)$coef[3,4] < 0.1) 
  {summary(model)$coef[3,1]} else {
      0}
} else {
  0
}
#  print(beta_d)
  
  beta_f  = 
if(length(summary(model)$coef[,1]) >= 4 ){
  if(summary(model)$coef[4,4] < 0.1) 
  {summary(model)$coef[4,1]} else {
      0}
} else {
  0
}

  lf = exp(beta_lp*log(1 - TPR) + beta_d*DIS + beta_f*FEA)
}


#(a)
#For Dominicks
print(lift_factor(D_d_f_lm, 0.15))
#For Jewel
print(lift_factor(J_d_f_lm, 0.15))

#(b)
#For Dominicks
print(lift_factor(D_d_f_lm, 0.15, 0.7))
#For Jewel
print(lift_factor(J_d_f_lm, 0.15, 0.7))

#(c)
#For Dominicks
print(lift_factor(D_d_f_lm, 0.15, 0.7, 1))
#For Jewel
print(lift_factor(J_d_f_lm, 0.15, 0.7, 1))

```
\newpage

## Question 4
Perform an ROI analysis of the three promotions, (a), (b), and (c), separately for the two retail accounts, Dominick’s and Jewel-Osco. The promotions last for one week. Your analysis should follow the approach that we took in class, not the version of this approach taken by Booz Allen Hamilton in the first part of the assignment. \newline
Note. Perform the analysis using units, not cases of Hellman’s mayo. You will need the following data for your analysis: \newline
• The regular price of the product at both accounts is $1.20. \newline
• The VCM for Hellman’s is $0.55 per unit. \newline
• The manufacturer fully pays for the shelf price reduction. E.g., if the shelf price is reduced from $1.20 to $1.00, the manufacturer pays for this TPR through a $0.20 per unit (off-invoice) allowance. \newline
• The fixed cost (MDF) for the promotion involving display only is $3,000 at Dominick’s and $5,000 at Jewel-Osco. The fixed cost for the promotion including feature and display is $4,500 at Dominick’s and $6,800 at Jewel-Osco. \newline
In order to estimate baseline sales, use the regression estimates and the regular price, and predict sales for display and feature = 0. \newline
Using these data, and the lift factors found in 3, you can then fill in the cells in the blueprint of a spreadsheet below, for each of the three promotions at both accounts. \newline
Consider both: \newline
• No stockpiling (purchase acceleration) \newline
• The case where 20 percent of the incremental units as predicted by the event lift are due to stockpiling (purchase acceleration), and hence not truly incremental \newline

```{r, fig.width = 6, fig.height = 3, fig.align = "center"}
ROI_Summary <- function(model, TPR = 0, DIS = 0, FEA = 0, fixed_payment_cost = 0, regular_price = 1.2, regular_margin = 0.55, Stockpiling = 0) {

baseline_units = exp(predict(D_d_f_lm, data.frame(price = regular_price, display = 0, feature = 0),
   type = "response"))

total_units = lift_factor(D_d_f_lm, TPR, DIS, FEA) * baseline_units

incremental_units = (total_units - baseline_units)

incremental_units_Stockpiling = incremental_units * Stockpiling

incremental_units_net = incremental_units - incremental_units_Stockpiling

promoted_price = (1 - TPR)*regular_price

promoted_margine = promoted_price - (regular_price - regular_margin)

incremental_contribution = promoted_margine * incremental_units_net
  
variable_cost = TPR * regular_price * baseline_units

event_cost = variable_cost + fixed_payment_cost

gross_contribution = incremental_contribution - event_cost

ROI = gross_contribution/event_cost

list("Baseline units" = baseline_units,
     "Incremental units" = incremental_units,
     "Total units" = total_units,
     "Precent with pa" = Stockpiling,
     "Incremental units with pa" = incremental_units_Stockpiling,
     "Incremental units net" = incremental_units_net,
     "Incremental contribution" = incremental_contribution,
     "Variable cost" = variable_cost,
     "Fixed payment cost" = fixed_payment_cost,
     "Event cost" = event_cost,
     "Event gross contribution" = gross_contribution,
     "ROI" = ROI)
}




#For Dominicks
#(a) 
df1 = data.frame(ROI_Summary(D_d_f_lm, 0.15))
#(b)
df2 = data.frame(ROI_Summary(D_d_f_lm, 0.15, 0.7, fixed_payment_cost = 3000))
#(c)
df3 = data.frame(ROI_Summary(D_d_f_lm, 0.15, 0.7, 1, fixed_payment_cost = 4500))

D_df = cbind(data.frame(t(df1)), data.frame(t(df2)), data.frame(t(df3)))
colnames(D_df) = c("Dominicks(a)", "Dominicks(b)", "Dominicks(c)")
print(D_df)

#Consider stockpiling is 20%
#(a) 
df1 = data.frame(ROI_Summary(D_d_f_lm, 0.15, Stockpiling = 0.2))
#(b)
df2 = data.frame(ROI_Summary(D_d_f_lm, 0.15, 0.7, fixed_payment_cost = 3000, Stockpiling = 0.2))
#(c)
df3 = data.frame(ROI_Summary(D_d_f_lm, 0.15, 0.7, 1, fixed_payment_cost = 4500, Stockpiling = 0.2))

D_20_df = cbind(data.frame(t(df1)), data.frame(t(df2)), data.frame(t(df3)))
colnames(D_20_df) = c("Dominicks(a)", "Dominicks(b)", "Dominicks(c)")
print(D_20_df)

#For Jewel
#(a) 
df1 = data.frame(ROI_Summary(J_d_f_lm, 0.15))
#(b)
df2 = data.frame(ROI_Summary(J_d_f_lm, 0.15, 0.7, fixed_payment_cost = 5000))
#(c)
df3 = data.frame(ROI_Summary(J_d_f_lm, 0.15, 0.7, 1, fixed_payment_cost = 6800))

J_20_df = cbind(data.frame(t(df1)), data.frame(t(df2)), data.frame(t(df3)))
colnames(J_20_df) = c("Jewel(a)", "Jewel(b)", "Jewel(c)")
print(J_20_df)

#Consider stockpiling is 20%
#(a) 
df1 = data.frame(ROI_Summary(J_d_f_lm, 0.15, Stockpiling = 0.2))
#(b)
df2 = data.frame(ROI_Summary(J_d_f_lm, 0.15, 0.7, Stockpiling = 0.2, fixed_payment_cost = 5000))
#(c)
df3 = data.frame(ROI_Summary(J_d_f_lm, 0.15, 0.7, 1, Stockpiling = 0.2, fixed_payment_cost = 6800))

J_20_df = cbind(data.frame(t(df1)), data.frame(t(df2)), data.frame(t(df3)))
colnames(J_20_df) = c("Jewel(a)", "Jewel(b)", "Jewel(c)")
print(J_20_df)
```
